MISUSES AND INACCURACIES OF PAGEL'S LAMBDA ML ESTIMATION METHODS

### 2020-04-24 Manuscript/Manuscript-2.tex
vsn 2

First, it presumes that values of \(\lambda\) can be precisely
estimated, as biological inferences regarding the strength of
phylogenetic signal depend on high accuracy in its estimation.
Therefore, understanding the precision in estimating \(\lambda\) is
paramount. One study (Boettiger et al. 2012) found that estimates of
Pagel's \(\lambda\) displayed less variation (i.e., greater precision)
when data were simulated on a large phylogeny (\(N=281\)) as compared to
a small one (\(N=13\)). From this observation it was concluded that
insufficient data (i.e., the number of species) was the underlying cause
of the increased variation across parameter estimates (Boettiger et al.
2012). Indeed, such a pattern is common with statistical estimators, as
summary statistics and parameters are often more precise with greater
sample sizes (Cohen 1988). However, this conclusion also assumes that
the precision in estimating \(\lambda\) remains constant across its
range (\(\lambda = 0 \to 1\)); an assumption that to date, has not been
verified. Thus, despite widespread use of Pagel's (1999) \(\lambda\) in
macroevolutionary studies, at present, we still lack a general
understanding of the precision with which \(\lambda\) can estimate
levels of phylogenetic signal in phenotypic datasets. \hfill\break

Second, while estimates of \(\lambda\) are within a bounded scale
(\(0\to1\)), this does not \emph{de-facto} imply that the estimated
values of this parameter correspond to the actual strength of the
underlying input signal in the data. For this to be the case,
\(\lambda\) must be a statistical effect size. Effect sizes are a
measure the magnitude of a statistical effect in data, represented on a
common scale (Glass 1976; Cohen 1988). Effect sizes have widespread use
in many areas of the quantiative sciences, as they represent measures
that may be readily summarized across datasets (e.g., meta-analysis:
Hedges and Olkin 1985; Glass 1976; Arnqvist and Wooster 1995), or
compared across datasets (e.g., Adams and Collyer 2016, 2019a).
Unfortunatley, not all model parameters and test statistics are effect
sizes, and thus many summary measures must first be converted to
standardized units (i.e., an effect size) for meaningful comparison (see
Rosenthal 1994). As a consequence, it follows that only if \(\lambda\)
is a statistical effect size can comparisons of estimates across
datasets be interpretable. For the case of \(\lambda\), this has not yet
been explored. \hfill\break

In this study, we evaluate the precision of Pagel's \(\lambda\) in
estimating known levels of phylogenetic signal in phenotypic data. We
use computer simulations with differing numbers of species, differently
shaped phylogenies, and differing input levels of phylogenetic signal,
to explore the degree to which \(\lambda\) correctly identifies known
levels of phylogenetic signal, and under what circumstances. We find
that while PGLS parameters (e.g., \(\beta\)) are accurately estimated
with the inclusion of phylogenetic signal, estimates of \(\lambda\) are
not. We also find that estimates of \(\lambda\) vary widely for a given
input value of phylogenetic signal, and that the precision in estimating
\(\lambda\) is not constant across the range of input signal, with
decreased precision when phylogenetic signal is of intermediate
strength. Additionally, the same \(\lambda_{est}\) may be obtained from
datasets containing vastly different input levels of phylogenetic
signal. Thus, \(\lambda\) is not a reliable effect size for measuring
the strength of phylogenetic signal. We subsequently derive a
standardized effect size for measuring the strength of phylogenetic
signal in phenotypic datasets, and apply the concept to two common
measures of phylogenetic signal: \(\lambda\) and \(Kappa\). Through
simulations across a wide range of conditions, we find that the
precision of effect sizes based on \(\lambda\) (\(Z_{\lambda}\)) are
less reliable than that those based on \(Kappa\) (\(Z_K\)), implying
that \(Z_K\) is a more robust effect size measure. Additionally, we
propose a two-sample test statistic that may be used to compare the
strength of phylogenetic signal among datasets. We conclude that
estimates of phylogenetic signal using Pagel's \(\lambda\) are often
inaccurate, and thus interpreting strength of phylogenetic signal in
phenotypic datasets based on this measure is compromised. By contrast,
effect sizes obtained from \(Kappa\) hold promise for characterizing
phylogenetic signal, and for comparing the strength of phylogenetic
signal across datasets.

@@

\hypertarget{the-precision-of-lambda-is-variable}{%
\subsection{\texorpdfstring{The Precision of \(\lambda\) is
Variable}{The Precision of \textbackslash lambda is Variable}}\label{the-precision-of-lambda-is-variable}}

We conducted a series of computer simulations to evaluate the precision
of Pagel's \(\lambda\). Our primary simulations were based on pure-birth
phylogenies; however, we also evaluated patterns on both balanced and
pectinate trees to determine whether tree shape affected our findings
(see Supporting Information). First we generated 50 pure-birth
phylogenies at each of six different tree sizes, ranging from 32 to 1024
taxa (\(n=2^5 - 2^{10}\)). Next, we rescaled the simulated phylogenies
by multiplying the internal branches by \(\lambda_{in} = 0.0 \to 1.0\)
using 21 intervals of 0.05 units, resulting in 1050 scaled phylogenies
at each level of species richness (\(n\)). Continuous traits were then
simulated on each phylogeny under a Brownian motion model of evolution
to obtain datasets with differing levels of phylogenetic signal, that
ranged from no phylogenetic signal (when \(\lambda_{in} =0\)), to
phylogenetic signal corresponding reflecting Brownian motion (when
\(\lambda_{in} =1\)). We then calculated the precision (variance:
\(\sigma^2_\lambda\)) of \(\lambda\) at each input level of phylogenetic
signal and at each level of species richness (\(n\)). \hfill\break

We also evaluated the precision of \(\lambda\) when estimated in PGLS
regression and ANOVA (i.e., \(Y\sim{X}\)). Here, an independent variable
\(X\) was simulated on each phylogeny under a Brownian motion model of
evolution (for PGLS regression). For phylogenetic ANOVA, random groups
(\(X\)) were obtained by simulating a discrete (binary) character on
each phylogeny. Next, the dependent variable was simulated in such a
manner as to contain a known relationship with \(X\) plus random error
containing phylogenetic signal. This was accomplished as:
\(Y=\beta{X}+\epsilon\). Here, the association between \(Y\) and \(X\)
was modeled using a range of values:
\(\beta=(0.0,0.25, 0.5, 0.75,1.0)\), and the residual error was modeled
to contain phylogenetic signal simulated under a Brownian motion model
of evolution: \(\epsilon=\mathcal{N}(\mu=0,\sigma=\mathbf{C})\): (see
Revell 2010 for a similar simulation design). The fit of the
phylogenetic regression was estimated using maximum likelihood, and
parameter estimates (\(\beta_{est}\) and \(\lambda_{est}\)) were
obtained. Precision estimates (\(\sigma^2_\lambda\)) at each input level
of phylogenetic signal and at each level of species richness (\(n\))
were then observed. All analyses were performed in R v3.6.0 (R Core Team
2019) using the packages \texttt{geiger} (Harmon et al. 2008),
\texttt{caper} (Orme et al. 2013), \texttt{phytools} (Revell 2012), and
\texttt{geomorph} (Adams and Otárola-Castillo 2013; Adams et al. 2020).
R-scripts are found in the Supporting Information. \hfill\break

\emph{Results.} We found that the precision of \(\lambda_{est}\) varied
widely across simulation conditions. Predictably, precision improved as
the number of species increased (Figure 1). This confirmed earlier
findings of Boettiger et al.~(2012), and adhered to parametric
statistical theory. However, in many cases the set of \(\lambda_{est}\)
spanned nearly the entire range of possible values (e.g., \(n=32\);
\(\lambda_{in}=0.5\): \(\lambda_{est}= 0.0\to 0.985\)), revealing that
estimates of \(\lambda\) were not a reliable indicator of input
phylogenetic signal. Importantly, the precision of \(\lambda_{est}\) was
not uniform across all levels of phylogenetic signal, with the worst
precision at intermediate levels of signal (\(\lambda_{in}\approx0.5\)),
and improved precision as input levels approaches 0 and 1 (i.e.,
\(\lambda_{in}\rightarrow0\) \& \(\lambda_{in}\rightarrow1\)). Thus,
estimates of \(\lambda\) were least reflective of the true input signal
at intermediate values. Additionally, even at large levels of species
richness, we found that the range of \(\lambda_{est}\) still encompassed
a substantial portion of possible values (e.g., \(n=512\);
\(\lambda_{in}=0.5\): \(\lambda_{est} = 0.32\to 0.68\)). Likewise, the
same \(\lambda_{est}\) could be obtained from datasets containing vastly
different input levels of phylogenetic signal (e.g., \(n=512\);
\(\lambda_{est} = 0.5\); \(\lambda_{in} = 0.25 \to 0.65\)). Results were
similar when \(\lambda\) was co-estimated with regression parameters in
PGLS regression (Figure 2). Here, regression parameters (\(\beta\)) were
accurately estimated, confirming earlier findings of Revell 2010 (2010)
(see Supporting Information). However, estimates of phylogenetic signal
were not, and the spread of \(\lambda_{est}\) was even broader tham that
observed when \(\lambda\) was estimated for only the dependent variable.
Taken together, these findings reveal that \(\lambda_{est}\) does not
precisely characterize observed levels of phylogenetic signal in
phenotypic datasets, and that biological interpretations of the strength
of phylogenetic signal based on \(\lambda\) may be highly inaccurate.
\hfill\break

@@

The above findings have several important implications for empirical
studies.

-Empirical examples: how interpretation can get folks ito trouble.

\hypertarget{a-standardized-effect-size-for-phylogenetic-signal}{%
\subsection{A Standardized Effect Size for Phylogenetic
Signal}\label{a-standardized-effect-size-for-phylogenetic-signal}}

-Derivation of effect size (expand on Adams and Collyer 2019 suggestion
that an effect size for phylogenetic signal is needed. The `gold
standard' of these is a standaredized effect size: (following the
meta-analytic literature beginning with Glass 1976). In other words, a
Z-score. So, how does Z work when based on lambda? On kappa? - Z-score.
could be Lambda or Kappa. Show it is Kappa -Comparing the strength of
physig - two sample Z-score

@@

Finally, for comparison we characterized the strength of phylogenetic
signal in each dataset using a standardized effect size (\(Z_K\): sensu
Adams and Collyer 2016, 2019a) based on \(Kappa\). As suggested by Adams
and Collyer (2019b), an effect size for phylogenetic signal may be
estimated as: \(Z_K=\frac{K_{obs}-\mu_K}{\sigma_K}\), where \(K_{obs}\)
was the observed \(Kappa\), and \(\mu_K\) and \(\sigma_K\) were the mean
and standard deviation of the empirical sampling distribution of values
obtained from the permutation distribution. \(Z_K\) describes the
strength of phylogenetic signal as a standard deviate from its sampling
distribution, and thus directly measures the strength of signal in a
manner that is comparable across datasets. Variation in the set of
\(Z_K\) at each input level of phylogenetic signal was then calculated
as an estimate of precision in \(Z_K\). However, because \(Z_K\) differs
in scale from \(\lambda\), we used a linear normalization to standardize
\(Z_K\) to a uniform distribution (\(0\rightarrow1\)), and estimated the
precision of \(Z_K\) from the normalized values. \hfill\break

@@

@@

@@

\textbf{Figure 2}. Precision of Pagel's \(\lambda\) when incorporated in
phylogenetic regression (\(|Y\sim X\)), across known levels of input
phylogenetic signal (\(\lambda_{in}\)) on phylogenies of various sizes.
As phylogenies increase in size, variation in \(\lambda_{in}\)
decreases; however the precision is not constant across the range of
input levels (\(\lambda_{in}: 0 \to 1\)), and is highest at intermediate
levels of phylogenetic signal. \hfill\break

@@

\singlespacing \textbf{Figure 2}. Precision of Pagel's \(\lambda\) when
incorporated in phylogenetic regression (\(|Y\sim X\)), across known
levels of input phylogenetic signal (\(\lambda_{in}\)) on phylogenies of
various sizes. As phylogenies increase in size, variation in
\(\lambda_{in}\) decreases; however the precision is not constant across
the range of input levels (\(\lambda_{in}: 0 \to 1\)), and is highest at
intermediate levels of phylogenetic signal.

>>>>

First, it presumes that values of \(\lambda\) can be precisely
estimated, as biological inferences regarding the strength of
phylogenetic signal depend on high accuracy in its estimation.
Therefore, understanding the precision in estimating \(\lambda\) is
paramount. One study (Boettiger et al. 2012) found that estimates of
Pagel's \(\lambda\) displayed less variation (i.e., greater precision)
when data were simulated on a large phylogeny (\(N=281\)) as compared to
a small one (\(N=13\)). From this observation it was concluded that
insufficient data (i.e., the number of species) was the underlying cause
of the increased variation across parameter estimates (Boettiger et al.
2012). Indeed, such a pattern is common with statistical estimators, as
summary statistics and parameters are often more precise at greater
sample sizes (Cohen 1988). However, this conclusion also assumes that
the precision of \(\lambda\) remains constant across its range
(\(\lambda = 0 \to 1\)); an assumption that to date, has not been
verified. Thus, despite widespread use of Pagel's (1999) \(\lambda\) in
macroevolutionary studies, at present, we still lack a general
understanding of the precision with which \(\lambda\) can estimate
levels of phylogenetic signal in phenotypic datasets. \hfill\break

Second, while estimates of \(\lambda\) are within a bounded scale
(\(0\to1\)), this does not \emph{de-facto} imply that the estimated
values of this parameter correspond to the actual strength of the
underlying input signal in the data. For this to be the case,
\(\lambda\) must be a statistical effect size. Effect sizes are a
measure the magnitude of a statistical effect in data, represented on a
common scale (Glass 1976; Cohen 1988). Effect sizes have widespread use
in many areas of the quantiative sciences, as they represent measures
that may be readily summarized across datasets as in meta-analysis
(Glass 1976; Hedges and Olkin 1985; Arnqvist and Wooster 1995), or
compared among datasets (e.g., Adams and Collyer 2016, 2019a).
Unfortunatley, not all model parameters and test statistics are effect
sizes, and thus many summary measures must first be converted to
standardized units (i.e., an effect size) for meaningful comparison (see
Rosenthal 1994). As a consequence, it follows that only if \(\lambda\)
is a statistical effect size can comparisons of estimates across
datasets be interpretable. For the case of \(\lambda\), this has not yet
been explored. \hfill\break

In this study, we evaluate the precision of Pagel's \(\lambda\) in
estimating known levels of phylogenetic signal in phenotypic data. We
use computer simulations with differing numbers of species, differently
shaped phylogenies, and differing input levels of phylogenetic signal,
to explore the degree to which \(\lambda\) correctly identifies known
levels of phylogenetic signal, and under what circumstances. We find
that while PGLS parameters (e.g., \(\beta\)) are accurately estimated
with the inclusion of phylogenetic signal, estimates of \(\lambda\) are
not. We also find that estimates of \(\lambda\) vary widely for a given
input value of phylogenetic signal, and that the precision in estimating
\(\lambda\) is not constant across the range of input signal, with
decreased precision when phylogenetic signal is of intermediate
strength. Additionally, the same \(\lambda_{est}\) may be obtained from
datasets containing vastly different input levels of phylogenetic
signal. Thus, \(\lambda\) is not a reliable estimate of the strength of
phylogenetic signal in phenotypic data. We subsequently derive a
standardized effect size for measuring the strength of phylogenetic
signal in phenotypic datasets, and apply the concept to two common
measures of phylogenetic signal: \(\lambda\) and \(Kappa\). Through
simulations across a wide range of conditions, we find that the
precision of effect sizes based on \(\lambda\) (\(Z_{\lambda}\)) are
less reliable than that those based on \(Kappa\) (\(Z_K\)), implying
that \(Z_K\) is a more robust effect size measure. Additionally, we
propose a two-sample test statistic that may be used to compare the
strength of phylogenetic signal among datasets, and provide an empirical
example to demonstrate its use. We conclude that estimates of
phylogenetic signal using Pagel's \(\lambda\) are often inaccurate, and
thus interpreting strength of phylogenetic signal in phenotypic datasets
based on this measure is compromised. By contrast, effect sizes obtained
from \(Kappa\) hold promise for characterizing phylogenetic signal, and
for comparing the strength of phylogenetic signal across datasets.

@@

\hypertarget{the-precision-of-lambda-is-variable}{%
\subsection{\texorpdfstring{\emph{The Precision of \(\lambda\) is
Variable}}{The Precision of \textbackslash lambda is Variable}}\label{the-precision-of-lambda-is-variable}}

We conducted a series of computer simulations to evaluate the precision
of Pagel's \(\lambda\). Our primary simulations were based on pure-birth
phylogenies; however, we also evaluated patterns on both balanced and
pectinate trees to determine whether tree shape affected our findings
(see Supporting Information). First we generated 50 pure-birth
phylogenies at each of six different tree sizes, ranging from 32 to 1024
taxa (\(n=2^5 - 2^{10}\)). Next, we rescaled the simulated phylogenies
by multiplying the internal branches by \(\lambda_{in}\), using 21
intervals of 0.05 units across its range
(\(\lambda_{in} = 0.0 \to 1.0\)), resulting in 1050 scaled phylogenies
at each level of species richness (\(n\)). Continuous traits were then
simulated on each phylogeny under a Brownian motion model of evolution
to obtain datasets with differing levels of phylogenetic signal, that
ranged from no phylogenetic signal (when \(\lambda_{in} =0\)), to
phylogenetic signal corresponding reflecting Brownian motion (when
\(\lambda_{in} =1\)). For each dataset we then estimated phylogenetic
signal (\(\lambda_{est}\)), and calculated the precision of \(\lambda\)
using the variance (\(\sigma^2_\lambda\)) across datasets at each input
level of phylogenetic signal and level of species richness. \hfill\break

We also evaluated the precision of \(\lambda\) when estimated in PGLS
regression and ANOVA (i.e., \(Y\sim{X}\)). Here, an independent variable
\(X\) was simulated on each phylogeny under a Brownian motion model of
evolution (for PGLS regression). For phylogenetic ANOVA, random groups
(\(X\)) were obtained by simulating a discrete (binary) character on
each phylogeny. Next, the dependent variable was simulated in such a
manner as to contain a known relationship with \(X\) plus random error
containing phylogenetic signal. This was accomplished as:
\(Y=\beta{X}+\epsilon\). Here, the association between \(Y\) and \(X\)
was modeled using a range of values:
\(\beta=(0.0,0.25, 0.5, 0.75,1.0)\), and the residual error was modeled
to contain phylogenetic signal simulated under a Brownian motion model
of evolution: \(\epsilon=\mathcal{N}(\mu=0,\sigma=\mathbf{C})\): (see
Revell 2010 for a similar simulation design). The fit of the
phylogenetic regression was estimated using maximum likelihood, and
parameter estimates (\(\beta_{est}\) and \(\lambda_{est}\)) were
obtained. Precision estimates (\(\sigma^2_\lambda\)) at each input level
of phylogenetic signal and level of species richness were then observed.
\hfill\break

All analyses were performed in R v3.6.0 (R Core Team 2019) using the
packages \texttt{geiger} (Harmon et al. 2008), \texttt{caper} (Orme et
al. 2013), \texttt{phytools} (Revell 2012), and \texttt{geomorph} (Adams
and Otárola-Castillo 2013; Adams et al. 2020). R-scripts are found in
the Supporting Information. \hfill\break

\emph{Results.} We found that the precision of \(\lambda_{est}\) varied
widely across simulation conditions. Predictably, precision improved as
the number of species increased (Figure 1). This confirmed earlier
findings of Boettiger et al.~(2012), and adhered to parametric
statistical theory. However, in many cases the set of \(\lambda_{est}\)
spanned nearly the entire range of possible values (e.g., \(n=32\);
\(\lambda_{in}=0.5\): \(\lambda_{est}= 0.0\to 0.985\)), revealing that
estimates of \(\lambda\) were not a reliable indicator of input
phylogenetic signal. Importantly, the precision of \(\lambda_{est}\) was
not uniform across all levels of phylogenetic signal, with the worst
precision at intermediate levels of signal (\(\lambda_{in}\approx0.5\)),
and improved precision as input levels approached the extremes of its
range (i.e., \(\lambda_{in}\rightarrow0\) \&
\(\lambda_{in}\rightarrow1\)). Thus, estimates of \(\lambda\) were least
reflective of the true input signal at intermediate values.
Additionally, even at large levels of species richness, we found that
the range of \(\lambda_{est}\) still encompassed a substantial portion
of possible values (e.g., \(n=512\); \(\lambda_{in}=0.5\):
\(\lambda_{est} = 0.32\to 0.68\)). Likewise, the same \(\lambda_{est}\)
could be obtained from datasets containing vastly different input levels
of phylogenetic signal (e.g., \(n=512\); \(\lambda_{est} = 0.5\);
\(\lambda_{in} = 0.25 \to 0.65\)). Results were similar when \(\lambda\)
was co-estimated with regression parameters in PGLS regression (Figure
2). Here, regression parameters (\(\beta\)) were accurately estimated,
confirming earlier findings of Revell 2010 (2010) (see Supporting
Information). However, estimates of phylogenetic signal were not, and
the spread of \(\lambda_{est}\) was even broader than that observed when
\(\lambda\) was estimated for only the dependent variable. Taken
together, these findings reveal that \(\lambda_{est}\) does not
precisely characterize observed levels of phylogenetic signal in
phenotypic datasets, and that biological interpretations of the strength
of phylogenetic signal based on \(\lambda\) may be highly inaccurate.
\hfill\break

@@

\hypertarget{a-standardized-effect-size-for-phylogenetic-signal}{%
\subsection{\texorpdfstring{\emph{A Standardized Effect Size for
Phylogenetic
Signal}}{A Standardized Effect Size for Phylogenetic Signal}}\label{a-standardized-effect-size-for-phylogenetic-signal}}

The results above demonstate that \(\lambda\) is not a reliable estimate
of the phylogenetic signal in phenotypic data. As such, biological
interpretations of the strength of phylogenetic signal, and comparisons
of the magnitude of such effects across datasets, are severely
compromised when based on this parameter. As an alternative, we propose
that summary estimates of phylogenetic signal be converted to effect
sizes for these purposes. A standardized effect size is found as:

\begin{align}
    Z_{\theta}=\frac{\theta_{obs}-E(\theta)}{\sigma_\theta}
\end{align}

where \(\theta_{obs}\) is the observed test statistic, \(E(\theta)\) is
its expected value under the null hypothesis, and \(\sigma_\theta\) is
its standard error (Glass 1976; Cohen 1988; Rosenthal 1994).
\(Z_{\theta}\) expresses the magnitude of the effect in \(\theta_{obs}\)
by transforming the original test statistic to a standard normal deviate
(Glass 1976; Kelley and Preacher 2012). Here, \(\theta_{obs}\) and
\(\sigma_\theta\) are estimated from the data, while \(E(\theta)\) is
obtained from the distribution of \(\theta\) derived from parametric
theory. However, recent advances in resampling theory (Collyer et al.
2015; Adams and Collyer 2016, 2019a) have shown that \(E(\theta)\) and
\(\sigma_\theta\) may also be obtained from an empirical sampling
distribution obtained from permutation procedures. \hfill\break

Adams and Collyer (2019b) recently suggested that the strength of
phylogenetic signal could be represented an effect size, obtained from
\(Kappa\) and its empirical sampling distribution from permutation. Here
we formalize that suggestion, and find an effect size as:

\begin{align}
    Z_{K}=\frac{K_{obs}-\hat\mu_K}{\hat\sigma_K}
\end{align}

Similarly, an effect size based on \(\lambda\) could be envisioned as:

\begin{align}
    Z_{\lambda}=\frac{\lambda_{obs}-0}{\hat\sigma_\lambda}
\end{align}

Note that under the null hypothesis, \(E(\lambda)=0\), a no phylogenetic
signal is expected under this condition (Freckleton et al. 2002).

\begin{itemize}
\tightlist
\item
  Z-score. could be Lambda or Kappa. Show it is Kappa -Comparing the
  strength of physig
\item
  two sample Z-score
\end{itemize}

@@

Finally, for comparison we characterized the strength of phylogenetic
signal in each dataset using a standardized effect size (\(Z_K\): sensu
Adams and Collyer 2016, 2019a) based on \(Kappa\).

Variation in the set of \(Z_K\) at each input level of phylogenetic
signal was then calculated as an estimate of precision in \(Z_K\).
However, because \(Z_K\) differs in scale from \(\lambda\), we used a
linear normalization to standardize \(Z_K\) to a uniform distribution
(\(0\rightarrow1\)), and estimated the precision of \(Z_K\) from the
normalized values. \hfill\break

@@

\leavevmode\hypertarget{ref-Collyer_et_al2015a}{}%
Collyer, M. L., D. J. Sekora, and D. C. Adams. 2015. A method for
analysis of phenotypic change for phenotypes described by
high-dimensional data. Heredity 115:357--365.

@@

\leavevmode\hypertarget{ref-Kelley2012}{}%
Kelley, K., and K. J. Preacher. 2012. On effect size. Psychological
Methods 17:137--152.

@@

\textbf{Figure 2}. Precision of Pagel's \(\lambda\) when incorporated in
phylogenetic regression (\(Y\sim X\)), across known levels of input
phylogenetic signal (\(\lambda_{in}\)) on phylogenies of various sizes.
As phylogenies increase in size, variation in \(\lambda_{in}\)
decreases; however the precision is not constant across the range of
input levels (\(\lambda_{in}: 0 \to 1\)), and is highest at intermediate
levels of phylogenetic signal. \hfill\break

@@

\singlespacing \textbf{Figure 2}. Precision of Pagel's \(\lambda\) when
incorporated in phylogenetic regression (\(Y\sim X\)), across known
levels of input phylogenetic signal (\(\lambda_{in}\)) on phylogenies of
various sizes. As phylogenies increase in size, variation in
\(\lambda_{in}\) decreases; however the precision is not constant across
the range of input levels (\(\lambda_{in}: 0 \to 1\)), and is highest at
intermediate levels of phylogenetic signal.
